Sorting out the 16s

### 2021-02-15 scripts/45_16s_sorting_out.Rmd
great slowly picking up the pace

u_meta_b %>% 
  count(toxicity)
```

>>>>

u_meta_b %>% 
  count(toxicity)
```
## merge the two pheno tables and then write out

```{r}
m <- m_meta_b %>% 
  select(-pt_id_old) %>% 
  rename(pt_id = mrn) %>% 
  select(-last_followup) %>% 
  mutate(center = 'M') %>% 
  mutate(icansgrade = as.character(icansgrade))

p <- u_meta_b %>%   
  mutate(time_group = 'Baseline') %>% 
  select(-sampleid) %>% 
  rename(sampleid = oligoid) %>% 
  select(-last_followup_day) %>% 
  mutate(center = 'P')  %>% 
  select(colnames(m))

combined <- bind_rows(m, p)
```

## also get the alpha diversity here

```{r}
get_table_from_database('asv_alpha_diversity_ag')

combined_join <- combined %>% 
  inner_join(asv_alpha_diversity_ag %>% 
               select(sampleid, simpson_reciprocal))

combined_join %>% 
  write_csv('../data/amplicon/stool/combined_2_meta.csv')
```
